---
title: "In Class Exercise 1" 
author: "Yudum Paçin"
date: "21 October 2022"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---
<style>
    body { 
    font-family: Calibri;
    text-align: justify;
    font-size: 11pt;
    }
</style>

### IN CLASS EXERCISE 1 {.unnumbered}

Install necessary packages

```{r install_packages, eval=FALSE}
install.packages("tidyverse")
install.packages("nycflights13")
```

Call necessary libraries
```{r call_libraries, message = FALSE}
library(tidyverse)
library(nycflights13)
```

In this exercise, we will explore planes dataset in nycflights13 library
planes, consists of construction information about  3,322 planes used for all flights departing NYC in 2013.

```{r data_first_look, message = FALSE}
glimpse(planes)
```

10 Most common models, manufacturers of the planes are,

```{r data_sort, message = FALSE}
planes %>% 
  group_by(model,manufacturer) %>%
  summarise(say=n()) %>%
  arrange(desc(say),10)
```
737-7H4 BOEING is the most common plane,
Let's have a look at this plane in detail

737-7H4 is a BOEING model only!, There is no other manufacturer. So, we can filter with "model" only.

```{r check_data, message = FALSE}
planes %>% 
  filter(model=='737-7H4' & manufacturer!='BOEING') 
```

In, what years 737-7H4 is constructed, and how many?

```{r common_by_year, message = FALSE}
planes %>% 
  filter(model=='737-7H4') %>%
  group_by(year) %>%
  summarise(say=n())
```
Since 1997, 737-7H4 is constructed and used in NYC Airlines. There are 6 planes having missing year values. In 2004, number of 737-7H4 planes is at the peak, after 2004 number of 737-7H4 planes are decreasing, but still it is the most common plane model in NYC flights.





